\section{Bitcoin's networking protocol}
The message transfer protocol used in Bitcoin is defined abstractly in Nakamoto's original publication \cite{Nakamoto} and further fleshed out in \texttt{bitcoind}, the reference implementation he provided. In this section, we will provide a high-level overview of the relevant portion of the protocol. %In particular, we will not discuss how new clients are bootstrapped, how initial blocks are downloaded, or how further peer connections are established. This leaves the standard relay protocol, which consists of four message types:

The standard relay protocol used to share blocks between clients contains four types of messages:

\begin{itemize}

\item \textit{inv}: When a transaction or block has been verified by a node, the node announces that the transaction or block is available by sending an \textit{inv} message to all of their neighbors.
\item \textit{getdata}: When a node receives an \textit{inv} message for a transaction or block that it does not already have a local copy of, it responds with a \textit{getdata} message asking for that block.
\item \textit{tx}: When a node receives a \textit{getdata} request for a given transaction, it responds with a \textit{tx} message containing the transaction.
\item \textit{block} When a node receives a \textit{getdata} request for a given block, it responds with a \textit{block} message containing the block.

\end{itemize}

A node will only propagate a block or transaction to its neighbors if it can verify it. Unverified transactions or blocks are not propagated. % TODO citation for this? Source code?

Partitions occur when two or more competing blockchain heads emerge. 
By itself, Bitcoin does not attempt to detect or mitigate partitions. If a partition appears due to two groups having different views of the current blockchain, both groups will continue operating independently and their state will diverge. If the divergence results in subnetworks that produce incompatible transaction histories, they will be unable to merge if the partition is later removed. Decker and Wattenhofer \cite{DeckerWattenhofer2013} observe that detection of network partitions may not be challenging and could be achieved through simple monitoring of the observed aggregate computational power in the network. As Bitcoin has grown in size and influence, such monitoring has begun to take place, and as of this writing it is possible to easily view the total network hashing rate via public websites \cite{sipa}.



